Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping

### 2018-04-24 stp/paper_aaai/main.tex
authors

\pdfinfo{
/Title (Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping)
/Author (Submission 1228)
/Keywords (Machine Lerning Application, Constraint Programming, Ontology, Relational, Steiner Tree)}
\setcounter{secnumdepth}{2}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping }
\author{Submission 1228}
\maketitle
\begin{abstract}
%% REWRITTEN:

>>>>

\pdfinfo{
/Title (Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping)
/Author (Submission)
/Keywords (Machine Lerning Application, Constraint Programming, Ontology, Relational, Steiner Tree)}
\setcounter{secnumdepth}{2}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping }
\author{Diego De U\~na$^1$ , Natalia Ruemelle$^2$, Graeme Gange$^1$, Peter Schachte$^1$ \and Peter J. Stuckey$^{1,2}$\\
$^1$Department of Computing and Information Systems --- The University of Melbourne\\
$^2$Data61, CSIRO\\
diegod1@student.unimelb.edu.au, Natalia Email, \{gkgange,schachte,pstuckey\}@unimelb.edu.au
}

\maketitle
\begin{abstract}
%% REWRITTEN:
